---
output:
  pdf_document: default
  html_document: default
---
# Introduction {#intro}

```{r setup, include=FALSE}
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}
shelf(
  bookdown,
  knitr,
  marinebon/ecoidx,
  plotly,
  quiet = T)

knitr::opts_chunk$set(echo = TRUE)
```

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

## Plots

```{r plot-ts}
p_static      <- ecoidx::plot_ts(ts1)
p_interactive <- ecoidx::plot_ts(ts1, add_icons = F) %>% 
  plotly::ggplotly()
```

### Static

```{r plot-ts-static, fig.cap = attr(p_static, "caption"), out.width='80%', fig.asp=.75, fig.align='center'}
p_static
```

### Interactive

```{r plot-ts-interactive, fig.cap = attr(p_static, "caption"), out.width='80%', fig.asp=.75, fig.align='center'}
p_interactive
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:plot-ts-static). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
